NIRCam Faint and Bright Flux Calibration Plan

### 2017-05-10 ms.tex
I added a few more notes about George's idea of a transfer all the way from alpha Cen A to P330-E.

Figure \ref{fig:sensitivityLadder} shows a schematic of the steps beginning with MSX calibrators (as bright as $K \sim -3$) to faint JWST standards ($K \sim 16$).
The methodology of the flux ladder is that only one change is made per step - either an instrument re-configuration is made on the same source or a new source is measured with the same instrument configuration.
As listed in Table \ref{tab:conversionSteps}, the direct calibrator would be observed in a neutral density square, subarray and medium band filter while using the coronagraphic pupil.
For the next step, this same instrument configuration will be used on a bright JWST standard, such as HD 37962 (G2 V, $K$=6.27).
Getting sufficient signal to noise (S/N$\gtrsim$200) on an intermediate JWST calibrator such as P-330E (G2 V, $K$=11.4) with the neutral density square in place would require unfeasibly long integration times so the bright calibrators are preferred for steps 2 and 3.

>>>>

Figure \ref{fig:sensitivityLadder} shows a schematic of the steps beginning with MSX calibrators (as bright as $K \sim -3$) to faint JWST standards ($K \sim 16$).
The methodology of the flux ladder is that only one change is made per step - either an instrument re-configuration is made on the same source or a new source is measured with the same instrument configuration.
As listed in Table \ref{tab:conversionSteps}, the direct calibrator would be observed in a neutral density square, subarray and medium band filter while using the coronagraphic pupil.
For the next step, this same instrument configuration will be used on a bright JWST standard, such as HD 37962 (G2 V, $K$=6.27).
Getting sufficient signal to noise (S/N$\gtrsim$200) on an intermediate JWST calibrator such as P-330E (G2 V, $K$=11.4) with the neutral density square in place would require long integration times so the bright calibrators are preferred for steps 2 and 3.

However, if sufficient time is available for calibration, it is possible to convert from an MSX standard to an intermediate JWST standard in one step.
To begin, the F212N filter could be selected in the filter wheel to observe a bright MSX star with the neutral density filter and Lyot pupil mask.
The same setup could be arranged on P330-E and observed for 7.5 hours to achieve a SNR=200.
If the F212N filter is used to observe P330-E with a full frame mode, it just barely is observable with 2 groups in RAPID mode before reaching full well saturation.
The advantage with this single step from subarray neutral density filters to full frame direct imaging is that it is fewer steps.
The disadvantage is that there would be a large disparity in detector well depth between the vertical and horizontal steps on this ladder.
